The Design and Implementation of the Synchronous Language \CEU

### 2016-09-27 paper.tex
(>) feasibility of the synchronous hypothesis

Note that Esterel supports declarations for mutually exclusive inputs which
cannot be simultaneous in the same reaction
(e.g., \code{relation A\#B\#C\#D\#E;})~\cite{esterel.primer}.
Making all inputs mutually exclusive and adopting the variable-length-tick
approach is equivalent to \CEU's notion of time, which can be seen as an
imposed restriction on the semantics of Esterel.

The synchronous hypothesis for \CEU holds if the reactions run faster than the 
rate of incoming input events.
Otherwise, the application continuously accumulates delays between the real 
occurrence and actual reaction of a given event.
%
This is also the case for the variable-length-tick approach of Esterel, since 
the more inputs to handle, the longer the reaction takes, and the more inputs 
accumulate for subsequent ticks.
%
For the fixed-length-tick approach of Esterel, a breach in the synchronous 
hypothesis causes timing violations, requiring \emph{worst case reaction time} 
analysis to infer appropriate tick lengths~\cite{esterel.fixed}.
% TODO-no: Such analysis is orthogonal

>>>>

Note that Esterel supports declarations for mutually exclusive inputs which
cannot be simultaneous in the same reaction
(e.g., ``\code{relation A\#B\#C\#D\#E;}'')~\cite{esterel.primer}.
Making all inputs mutually exclusive and adopting the variable-length-tick
approach is equivalent to \CEU's notion of time, which can be seen as an
imposed restriction on the semantics of Esterel.

The synchronous hypothesis for \CEU holds if the reactions run faster than the 
rate of incoming input events.
Otherwise, the application continuously accumulates delays between the real 
occurrence and actual reaction of a given event (we discuss implementation
considerations in Sections~\ref{sec.impl.single}~and~\ref{sec.impl.environment}).
%
This is also the case for the variable-length-tick approach of Esterel, since 
the more inputs to handle, the longer the reaction takes, and the more inputs 
accumulate for subsequent ticks.
%
For the fixed-length-tick approach of Esterel, a breach in the synchronous 
hypothesis causes timing violations, requiring \emph{worst case reaction time} 
analysis to infer appropriate tick lengths~\cite{esterel.fixed}.
% TODO-no: Such analysis is orthogonal
